### 2022-05-26 README.Rmd
small enhancement
updated readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimation of Population Density for the prehistoric Swiss Plateau using a Hierarchical Bayesian Poisson Regression Model"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/MartinHinz/bayesian.demographic.reconstruction.2021/master?urlpath=rstudio)

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: manuscript](/manuscript): R Markdown source document
    for manuscript.
  - [:file\_folder: paper](/paper): A rendered version, of the manuscript
    `paper.docx` and `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: analysis](/analysis): R Markdown source document
    for the actual analysis. Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: code](/code): Functions used in the analysis.
  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: figures](/figures): Plots and other illustrations

@@

@@

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Bayesian inference of prehistoric population dynamics from multiple proxies: a case study from the Swiss plateau"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/MartinHinz/bayesian.demographic.reconstruction.2022/master?urlpath=rstudio)

@@

> Hinz, M., Roe, J., Laabs, J., Heitz, C., Kolar, J. (2022). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Hinz, M., Roe, J., Laabs, J., Heitz, C., Kolar, J. (2022). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Hinz, M., Roe, J., Laabs, J., Heitz, C., Kolar, J., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: manuscript](/manuscript): R Markdown source document
    for manuscript.
  - [:file\_folder: paper](/paper): A rendered version, of the manuscript
    `paper.docx` and `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: analysis](/analysis): R Markdown source document
    for the actual analysis. Includes code to reproduce the figures and tables
    generated by the analysis. You can look at the [Github-Markdown Version](/analysis/analysis.md)
    for a rendered version of the analytical run incl. figures.
  - [:file\_folder: code](/code): Functions used in the analysis.
  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: figures](/figures): Plots and other illustrations

@@

To perform the actual analysis, we recommend a powerful computer with a
multi-core processor, ideally with the Linux operating system, which has
at least 64GB RAM memory. In addition, a hard disk space of at least 5GB
should be reserved for the process.

@@

**Text, code and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
